### 2018-07-16 manuscript.rmd
preliminary writing

@@

Phylogenetic signal (Blomberg 2003)
fitContinuous (geiger), BM, EB, OU.
Adams geomorph
phytools ppca, pgls, phyl.anova

@@

@@

Fulbright Spain. NSF Waterman Award. NSF siphweb project. Yale Institute of Biospehric Studies. Crew of R/V Western Flyer.

@@

Siphonophores are... [@Mackie:1987uy].

>>>>

Tentacles from the studied specimens were dissected, dehydrated in a series of ethanol dilutions (25% in PBS, 50% in PBS, 75% in water, 100%), cleared in methyl salicylate or d-limonene, and mounted in plastic slides (Canada balsam, Cytoseal, or Permount). Slides were imaged using laser scanning confocal microscopy and differential interference contrast (DIC) microscopy. Images were measured using Fiji-ImageJ.

The characters measured for this study are described in Supplementary Table SXX. Homology assumptions for nematocyst supertypes (heteroneme, haploneme, rhopaloneme, and desmoneme) and tentillum structures (involucrum, elastic strand, pedicle, cnidoband) were informed by positional, developmental, and morphological criteria.

@@

All phylogenetic statistical analyses were carried out in the programming environment R (cite). Phylogenetic signal in each of the measured characters was calculated using Blomberg’s K (Blomberg 2003).

fitContinuous (geiger), BM, EB, OU.
Adams geomorph
phytools ppca, pgls, phyl.anova

@@

High speed footage (1000-3000 fps) of tentillum and nematocyst discharge was recorded on live siphonophore specimens using a Phantom Miro 320S camera mounted on a stereoscopic microscope. Specimens were collected by SCUBA divers and the remotely operated underwater vehicle Doc Ricketts during expeditions onboard the R/V Western Flyer. Tentillum and nematocyst discharge were elicited mechanically using a fine metallic pin. Video footage was analyzed using Phantom PCC software.

@@

This work was funded by the Society of Systematic Biologists Graduate Student Award, the NSF Waterman Award, and the Yale Institute of Biospheric Studies Doctoral Pilot Grant. ADS was supported by a Fulbright Spain scholarship. We thank Philip R. Pugh for his assistance in the identification of specimens. We also wish to thank the crew of the R/V Western Flyer.

@@
